%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%--------------- modified by G. Carminati on 2014-09-19 -----------------

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

% to use FontAwesome --- needs to be installed from 
\usepackage{fontawesome}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Giada}{Carminati}{ % Your name
\vspace{-5pt} \begin{center}Irvine, CA \end{center} \vspace{-10pt}
\faEnvelope ~ \href{mailto:giadalcarminati@gmail.com}{giadalcarminati@gmail.com} \textbullet{} \faPhone ~ (949) 419-7023 \\ % Your contact information
\faGithub ~ \href{https://github.com/giadac}{giadac} \textbullet{}
\faLinkedinSign ~ \href{https://www.linkedin.com/in/giadacarminati}{giadacarminati} \textbullet{}
\faHome ~ \href{https://webfiles.uci.edu/gcarmina}{webfiles.uci.edu/gcarmina} \\ 
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.29\textwidth} % The left column takes up 29% of the text width of the page
%------------------------------- original format ------------------------------------
%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Languages}
%\location{Over 5000 lines:}
C++ \textbullet{} C \textbullet{} Shell Scripting \textbullet{} Python \\ 
 MATLAB (some exposure) \\ 

\subsection{Tools}
UNIX/Linux \textbullet{} MySQL \textbullet{} SciPy Stack \\
Natural Language Processing (NLTK) \\
Flask \textbullet{} Bootstrap \textbullet{} jQuery \\
\LaTeX\ \textbullet{} ROOT \\

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{University of Bologna}

\descript{Ph.D. in Physics}
\location{May 2010 | Bologna, Italy}

\sectionspace % Some whitespace after the section

\descript{M.Sc. in Physics} 
\small{(5-year degree equivalent to B.S. + M.Sc.)}\\
\location{Oct 2005 | Bologna, Italy}

\sectionspace % Some whitespace after the section
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Coursera}
- Machine Learning \\

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Graduate}
- Advanced C++ and Object-oriented Programming \\
- Computer Networks \\ 
- Advanced Numerical and Computer Methods for Particle Physics \\

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Undergraduate}

- Probability and Statistics \\
- Numerical Methods \\
- Data Analysis for Physics \\
- Unix Tools and Scripting \\
- C++ and Object-oriented Programming \\

%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Insight Data Science}
\descript{Fellow}

\location{Sep 2014 | Palo Alto, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Created \textit{WhoDoesMyHair.com}, a web application to recommend the highest rated hair stylists in hair salons.
\item Utilized Python and MySQL to parse, store and query the Yelp Academic Dataset.
\item Built custom recommendation engine applying the Python Natural Language Processing toolkit (NLTK) and the Stanford Named Entity Recognizer (NER).
\item Deployed interactive front-end with Flask, Bootstrap and jQuery, hosted on AWS.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{University of California, Irvine}
\descript{Postdoctoral Researcher}

\location{2010 – 2014 | Irvine, CA}
\begin{tightitemize}
\item Designed an innovative online software trigger to detect neutrino particles coming from the core of the Sun for a physics experiment in Japan.
\item Coordinated the software engineering team in Japan for installation and integration of the trigger in the online data acquisition system.
%\item Selected hardware components and network solutions to transfer 20~TB/day of data in real time.
\item Developed C++ algorithms to trigger and reconstruct physics events, including data cleaning and data selection using maximum likelihood methods.
\item Created software in C++ and bash script to monitor online network performance of the trigger system and to detect disruptions in data acquisition.
\item Designed C++ software using statistical analysis based on linear regression techniques to validate neutrino oscillation models.
\item Developed graphical software in C++ and ROOT (object-oriented C++ framework for high energy physics) to visualize trigger algorithm performance. 
\item Co-authored 22 peer-reviewed journal articles with a total of 480 citations and presented findings at 4 international conferences. 
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{University of Bologna and INFN}
\descript{Research Assistant}

\location{2005 – 2010 | Bologna, Italy}
\begin{tightitemize}
\item Created, developed and maintained \href{https://github.com/giadac/MUPAGE}{\textit{MUPAGE}}: a novelty Monte Carlo simulation software package in C++ to simulate particles produced in the atmosphere and arriving on an underwater neutrino telescope.
\item Mass-produced and analyzed Monte Carlo events for an astrophysics experiment in France, using C++ and ROOT. 
\item Performed graphical and statistical analysis based on linear regression to constrain astrophysics models for particle acceleration in the universe, using C++ and ROOT.
\item Co-authored 11 peer-reviewed journal articles with a total of 206 citations and presented findings at 2 international conferences.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{NIKHEF}
\descript{Visiting Research Assistant}

\location{2008 – 2009 | Amsterdam, The Netherlands}
\begin{tightitemize}
\item Designed a classification algorithm in C++ and ROOT to distinguish between different particles.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research
%------------------------------------------------

%\section{Research}
  
%------------------------------------------------
% Awards
%------------------------------------------------

%\section{Awards} 
%
%\begin{tabular}{rll}
%2012 & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\ %example
%2011 & National & Indian National Mathematics Olympiad (INMO) Finalist \\	%example
%\end{tabular}
%
%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

%\section{Societies} 
%
%\begin{tabular}{rll}
%2014 & National & The Global Leadership and Education Forum (tGELF)\\  %example
%\end{tabular}
%
%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}